### 2011-12-04 report/paper.tex
starting paper

\documentclass[10pt, twocolumn]{article}
\usepackage[margin=1in]{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{Analyzing Encrypted Web Traffic with Single- and Multi-Class SVMs}
\author{Emily Stark}
\date{\today}                                          % Activate to display a given date or no date

\begin{document}
\maketitle
%\section{}
%\subsection{}

\section{Introduction}
Web users, especially those in regions with censored 
Internet access, often use encryption in conjunction 
with anonymizing proxies to conceal which website 
they are visiting. For example, a user whose government 
restricts access to \texttt{www.facebook.com} can choose a 
proxy in an uncensored region, and use that proxy to 
forward encrypted HTTP requests and responses to and 
from Facebook. In theory, the censoring entity cannot determine from 
the user's encrypted traffic that the user is visiting 
Facebook. However, encryption does not conceal the direction, 
size, and timing of the packets that a user's web browsing 
generates. In practice, this small amount of information can 
be enough to determine the website that the user is visiting.

\end{document}

### 2011-12-05 report/paper.tex
intro and related work

@@
 they are visiting. For example, a user whose government 
-restricts access to \texttt{www.facebook.com} can choose a 
+restricts access to \texttt{https://www.facebook.com} can choose a 
 proxy in an uncensored region, and use that proxy to 
@@
 
+This problem is naturally phrased as a supervised learning 
+problem. Given a set of packet traces, where each trace is labelled 
+with the website that a user visited to generate it, we would 
+like to determine the website that a user visited to generate a new, 
+unlabeled trace. The point of training such a classifier is not 
+necessarily to make it easier for a censor to do its job, but rather 
+to understand the security guarantees that a user gets from using 
+an anonymizing proxy to forward encrypted web traffic, as well as 
+the effectiveness of proposed defenses against traffic analysis. 
+One such proposed defense is to generate a background request to a 
+random website for every encrypted request to a sensitive website~\cite{torfingerprinting}. 
+This defense, which I will refer to as the random-visit defense, 
+purportedly confuses the classifier by the addition of random 
+noise to the traffic generated by a visit to a sensitive website.
+
+In this project, I applied support vector machine (SVM) classifiers 
+to the problem of determining the source website of a stream of 
+encrypted web traffic. My goals were 1.) to train a SVM to 
+effectively classify traces of encrypted packets into their source 
+websites, and 2.) to show that SVMs can be used to break the random-visit 
+defense described above. While SVMs have been used before for 
+encrypted traffic analysis~\cite{SOMETHING}, the random-visit defense 
+is a very recent proposal and has not been well-studied yet.
+
+Previous work classifies encrypted traffic analysis into two settings: 
+closed world and open world. In the closed world setting, we assume that 
+the user visits one of a small number of websites over an encrypted, 
+anonymized connection, and the censor wishes to determine which website 
+the user is visiting. In the open world problem, which is much harder, the 
+censor has a small list of offensive websites that it wishes to block, but 
+the user might visit any website on the Internet. The censor wishes to 
+recognize when the user is visiting one of the offensive websites, and which 
+of the offensive websites is being visited. I used SVM-based techniques to 
+perform traffic analysis in both settings.
+
+Below I summarize the tasks that I completed for this project.
+\begin{itemize}
+\item \textbf{Data generation and preprocessing.} I generated packet 
+traces of visits to HTTPS websites, both with and without random 
+background visits. From these traces, I generated a feature vector for 
+each visit. This process is described in more detail in Section~\ref{sec:data}. 
+\item \textbf{Training binary and multiclass SVMs.} I used the 
+generated data to train several types of SVMs from the Python scikits-learn 
+library~\cite{sklearn}. These included a binary SVM, as well as one-vs-all
+and one-vs-one multiclass SVMs based on a binary SVM. I used $k$-fold cross-validation 
+to determine the SVM parameters.
+\item \textbf{Implementing a multiclass SVM and a single-class SVM for anomaly detection.} 
+I built a multiclass SVM using the Python \texttt{cvxopt} library~\cite{cvxopt}, 
+trained it, and measured the classification accuracy. To investigate the 
+open-world setting, I also built and trained a single-class SVM to perform 
+anomaly detection.
+\end{itemize}
+
+All the code that I wrote for this project is available online~\cite{github}.
+
+\section{Related Work}
+
+Much previous work has analyzed encrypted traffic to reveal the destination website or 
+even uncover sensitive information entered by the user on a HTTPS website. Early
+approaches simply fingerprinted websites by recording the sizes of objects generated 
+by a visit to the website~\cite{safeweb}. Since then, various machine learning 
+and data mining techniques, such as Jaccard coefficients and multinomial naive Bayes classifiers,
+have been applied to the encrypted traffic analysis problem~\cite{herrmann,liberatore}. 
+A recent work showed that SVMs are an effective traffic analysis technique~\cite{tor}, even 
+against protocols such as Tor (an anonymity network) that employ pipelining, which makes 
+traffic analysis more difficult. This work proposed the random-visit defense discussed above. In 
+this project I investigated the effectiveness of the random-visit defense in analyzing 
+SSL-encrypted web traffic.
+
 \end{document}

### 2011-12-06 dim_reduction.py
Added custom dimensionality reduction since PCA makes no sense in this application. Also various bug fixes and refactoring.

@@ -1,0 +1,204 @@
+import math, os
+from feature_vectors import (load_feature_vectors, get_target_sites,
+                             select_test_set, scale,
+                             select_cross_validation_subsets)
+from multiclass_on_binary_svm import classify
+import json
+import shutil
+import sys
+from multiclass_svm import SVM_fit, SVM_classify
+
+# nb is number of blocks to divide each packet trace into
+# e is measured in bytes
+def reduce(X_multi, X_single, n_features, nb, e):
+    # 3 features per packet
+    if len(X_multi[0]) % 3 != 0 or len(X_single[0]) % 3 != 0:
+        return []
+
+    # Precompute the total number of packets of each length and direction 
+    # in each block of each single visit.
+    print "Precomputing..."
+    score_lookup = {}
+    for i in range(0, nb):
+        sl = {0: {}, 1: {}}
+        for x in X_single:
+            # Get the i'th block of x
+            lx = 0
+            try:
+                lx = x.index(-1)
+            except:
+                lx = len(x)
+
+            ppb = (lx / 3) / nb # number of packets divided by number blocks
+            if i == nb - 1:
+                # last block eats up all leftover packets
+                block = x[ppb * i * 3 : lx]
+            else:
+                block = x[ppb * i * 3 : ppb * i * 3 + ppb * 3]
+
+            lp = len(block) / 3
+            for j in range(lp):
+                direction = block[j * 3 + 1]
+                length = block[j * 3 + 2]
+                if (sl[direction].has_key(length)):
+                    sl[direction][length] = sl[direction][length] + 1
+                else:
+                    sl[direction][length] = 1
+        score_lookup[i] = sl
+            
+    # Now we can compute the score of each feature in each vector in X_multi
+
+    Xnew = []
+    for x in X_multi:
+        scores = [] # a score for each packet
+        try:
+            lx = x.index(-1)
+        except:
+            lx = len(x)
+
+        np = lx / 3
+        ppb = np / nb
+        for i in range(np):
+            # figure out which block we're in
+            try:
+                b = i / ppb
+            except:
[…]

### 2011-12-06 anomaly_detection.py
add anomaly detection to dimensionality reduction test harness

@@ -5,7 +5,7 @@ from numpy import *
 import cmath
 
 def rbf(Xi, Xj):
-    beta = 0.0025
+    beta = 0.005
     norm = sum(map(lambda (xi, xj): (xi-xj)**2, zip(Xi, Xj)))
     return cmath.exp(-1*beta * norm).real
 
@@ -63,7 +63,7 @@ def AnomDet_fit(X, v, K = linK):
         h[i, 0] = 1.0/(v*n)
         A[0, i] = 1.0
 
-    solvers.options['maxiters'] = 500
+    solvers.options['show_progress'] = False
     sol = solvers.qp(cvxopt.matrix(P), cvxopt.matrix(q),
                      cvxopt.matrix(G), cvxopt.matrix(h),
                      cvxopt.matrix(A), cvxopt.matrix(b))

### 2011-12-06 dim_reduction.py

@@ -7,6 +7,14 @@ import json
 import shutil
 import sys
 from multiclass_svm import SVM_fit, SVM_classify
+from anomaly_detection import AnomDet_fit, AnomDet_classify, rbf
+
+def translate(translateDims, X):
+    Xnew = []
+    for x in X:
+        Xnew.append(map(lambda (i, xi):
+                            xi + translateDims[i], enumerate(x)))
+    return Xnew
 
 # nb is number of blocks to divide each packet trace into
 # e is measured in bytes
@@ -103,12 +111,16 @@ def reduce(X_multi, X_single, n_features, nb, e):
 
 def multiclass_svm_crossvalidate(X, Y, labels, c):
     iters = select_cross_validation_subsets(X, Y, 6)
-    for d in iters:
-        X = d["train"][0]
-        Y = d["train"][1]
-        testX = d["test"][0]
-        testY = d["test"][1]
-        multiclass_svm(X, Y, testX, testY, labels, c)
+    crange = [0.000001, 0.00001, 0.0001, 0.001, 0.01, 0.1,
+              1.0, 10.0, 100.0, 1000.0]
+    for c in crange:
+        print "C=%f"%c
+        for d in iters:
+            X = d["train"][0]
+            Y = d["train"][1]
+            testX = d["test"][0]
+            testY = d["test"][1]
+            multiclass_svm(X, Y, testX, testY, labels, c)
 
         
 def multiclass_svm(X, Y, testX, testY, labels, c=1.0):
@@ -137,11 +149,75 @@ def multiclass_svm_test(X, Y, labels, c, ntests):
     X, Y, testX, testY = select_test_set(X, Y, ntests)
     multiclass_svm(X, Y, testX, testY, labels, c)
 
+def monb_crossvalidate(X, Y, c, onevone):
+    iters = select_cross_validation_subsets(X, Y, 6)
+    #crange = [0.000001, 0.00001, 0.0001, 0.001, 0.01, 0.1,
+    #          1.0, 10.0, 100.0, 1000.0]
+    crange = [1.0]
+    for c in crange:
+        print "C=%f"%c
+        for d in iters:
+            X = d["train"][0]
+            Y = d["train"][1]
+            testX = d["test"][0]
+            testY = d["test"][1]
+            classify(X, Y, testX, testY, onevone, c)
+
 def monb_test(X, Y, c, onevone, ntest):
     X, Y, testX, testY = select_test_set(X, Y, ntest)
[…]

### 2011-12-06 report/paper.tex
filling in paper

@@
 \usepackage{epstopdf}
+\usepackage{subfigure}
 \DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
@@
 This defense, which I will refer to as the random-visit defense, 
-purportedly confuses the classifier by the addition of random 
+attempts to confuse the classifier by the addition of random 
 noise to the traffic generated by a visit to a sensitive website.
@@
 of the offensive websites is being visited. I used SVM-based techniques to 
-perform traffic analysis in both settings.
+perform traffic analysis in both a very small closed-world setting and an 
+open-world setting.
 
@@
 library~\cite{sklearn}. These included a binary SVM, as well as one-vs-all
-and one-vs-one multiclass SVMs based on a binary SVM. I used $k$-fold cross-validation 
+and one-vs-one multiclass SVMs based on a binary SVM. I implemented $k$-fold cross-validation 
 to determine the SVM parameters.
 \item \textbf{Implementing a multiclass SVM and a single-class SVM for anomaly detection.} 
-I built a multiclass SVM using the Python \texttt{cvxopt} library~\cite{cvxopt}, 
-trained it, and measured the classification accuracy. To investigate the 
+I built a multiclass SVM using the Python \texttt{cvxopt} library~\cite{cvxopt}.
+ To investigate the 
 open-world setting, I also built and trained a single-class SVM to perform 
 anomaly detection.
+\item \textbf{Designing and implementing a custom dimensionality reduction algorithm.} 
+Because \texttt{cvxopt} does not scale to very large problems, the feature vectors from the 
+packet traces were too large to run on the multiclass and single-class SVMs that I built. 
+I designed a feature selection algorithm that uses data from website visits without the 
+random-visit defense to select features for the data generated using the random-visit defense.
 \end{itemize}
@@
 
-\section{Related Work}
+\section{Related work}
 
@@
 
+\section{Data generation and preprocessing}
+
+In this paper, I will refer to a \textit{target site} as one of the HTTPS websites that a censoring 
+entity wants to block, and that a user tries to visit via an anonymizing proxy.
+ The target site is the label in the classification 
+problem. The \textit{background site} is the random website loaded in the background when a 
+user is using the random-visit defense.
+
+I generated two data sets for this project. The \textit{single-visit} data set consists of packet 
+traces from individual visits to a small set of target sites. The \textit{multi-visit} data set 
+consists of packet traces from individual visits to a small set of target sites, where each visit 
+happened concurrently with a visit to a random background site.
+
+I used 8 popular HTTPS websites (two banks, two file sharing applications, two social networks, 
+Google, and the Tor website) as target sites. The list of websites is located in \texttt{gen\_data.py}.
+In future, this work could be made much more convincing by increasing the number of target sites 
+to several hundred, but for this project I limited the closed-world setting to a few websites 
+because of limited computational resources. (I ran all experiments on my Macbook Pro laptop, and 
+for some classifiers, even with the small list of target sites, I had to limit the amount of data 
+used in training in order to not run out of memory. I discuss this limitation in greater detail 
+in Section~\ref{sec:multiclassimplementation}.)
+
+The background sites were chosen randomly from a list of 5000 of the most popular websites~\cite{alexa}. 
+While the background sites were visited over HTTP, I only used information such as packet timings and 
+lengths that would be available if HTTPS background sites were used. A real deployment of the 
+random-visit defense would use HTTPS-enabled sites as background sites; I only used HTTP sites as 
+background sites in this project because a large list of HTTPS websites was not readily available.
+
+\subsection{Data generation}
+
+For the single-visit data set, I wrote a Python script (\texttt{gen\_data.py}) to visit each site 
+in the list of target sites 30 times and record a packet trace with \texttt{tcpdump}. Each visit 
+occurred in a new instance of Google Chrome (in incognito mode, to prevent the browser from 
+using cached resources in subsequent visits).
+
+For the multi-visit data set, I modified \texttt{gen\_data.py} to, on each target site visit, 
+simultaneously open a second tab and load a randomly selected background site in that tab. For the 
+multi-visit data set, I recorded 60 visits to each target site instead of 30, since the multi-visit 
+data set presents a harder classification problem and therefore having more training data is helpful.
+
+\subsection{Preprocessing packet traces into feature vectors}
+\label{sec:preprocessing}
+
+\texttt{preprocess.py} uses \texttt{tcpdump} to parse the raw packet traces, and then translates 
+each target site visit into a feature vector. I defined three features for each recorded packet: the 
+time relative to the time of the first packet in the trace, the direction of the packet (to or from 
+the user's machine), and the length of the packet. I padded each vector with $-1$ values so that all 
+feature vectors in each data set were the same length. This selection of features led to large vectors 
+with several thousand features. For the classifiers that were unable to handle such large feature vectors 
+(my implementations of a multiclass SVM and a single-class SVM for anomaly detection, both using 
+\texttt{cvxopt}), I designed and implemented a dimensionality reduction algorithm that I describe in 
+Section~\ref{sec:dimred}.
+
+\section{SVMs in the closed world setting}
+
+For the closed world setting, I compared three multiclass SVMs:
+\begin{itemize}
+\item a one-vs-one multiclass SVM implemented in the scikits-learn library,
+\item a one-vs-all multiclass SVM implemented in the scikits-learn library,
+\item a multiclass SVM that I implemented using \texttt{cvxopt} (the implementation is 
+described in Section~\ref{sec:multiclassimplementation}).
+\end{itemize}
+
+I investigated the performance of these SVMs on both the single-visit and multi-visit data. 
+The training data was a list of feature vectors, where each feature vector corresponds to a 
+packet trace from a visit to a target site, as described in Section~\ref{sec:preprocessing}.
+
+I implemented $k-$fold cross-validation for each SVM to choose parameters. I also used 
+cross-validation to observe how the classifier's performance improves with the addition of more data 
+and how it suffers when more classes are introduced. Data from the cross-validation process is shown 
+in Section~\ref{sec:crossvalidation}.
+
+\subsection{Multiclass SVM implementation}
+\label{sec:multiclassimplementation}
+
+\subsection{Cross-validation for parameter tuning}
+\label{sec:crossvalidation}
+
+\begin{figure*}
+\begin{center}
+\subfigure[Single-visit data with full dimensionality.]{
+\includegraphics[scale=0.6]{graphs/single_visit_c.png}
+\label{fig:kfoldc-single}
+}
+\subfigure[Multi-visit data with dimensionality reduced to 50 features.]{
+\includegraphics[scale=0.6]{graphs/multi_visit_c.png}
+\label{fig:kfoldc-multi}
+}
+\caption{$k$-fold cross-validation results (with $k=6$) for tuning $c$, the cost associated with 
+each slack variable. The smaller size of the training data for the multiclass SVM is due to 
+limited computational resources.}
+\label{fig:kfoldc}
+\end{center}
+\end{figure*}
+
+\subsection{Performance results and analysis}
+
+\textbf{TODO: insert perf results}
+
+I briefly explored using the radial basis function as a kernel in the one-versus-one multiclass 
+SVM, but I could not find parameters that outperformed the linear kernel. For example, using $k$-fold 
+cross-validation with $k=6$ and the multi-visit data with 30 visits per target site, the best choice of 
+parameters that I was able to find for the linear and RBF kernels led to average performance of about 
+$30\%$ correct for both kernels. Assuming that I didn't miss some better choice of parameters for the 
+RBF kernel, this result suggests that the data is mostly linearly separable with outliers: the RBF kernel 
+does no better than the linear kernel, and it can do worse by overfitting.
+
+\section{A single-class SVM for the open world setting}
+
+For the open world setting, I implemented a single-class SVM with kernels, using the 
+\texttt{cvxopt} library.
+
+\subsection{Single-class SVM implementation}
+
+\subsection{Cross-validation for parameter tuning}
+
+\subsection{Performance results and analysis}
+
+\section{Dimensionality reduction}
+\label{sec:dimred}
+
+Table~\ref{tab:dimred-kfold} shows a SVM's performance as the number of features varies. The dimensionality 
+reduction algorithm definitively increases performance over the original feature vectors, and performance 
+seems to improve as the number of features gets smaller. This suggests that there are a small number of 
+packets that distinguish each target website, and the dimensionality reduction algorithm is effective at 
+extracting these features while removing noise.
+
+\begin{table}
+\caption{$k$-fold cross-validation performance of a one-vs-one multiclass SVM as the dimensionality of 
+the data is varied. $c$ is fixed at $1.0$ and $k$ is fixed at $6$. The data is the multi-visit data set 
+with 30 visits to each target site.}
+\begin{center}
+\begin{tabular}{|r|r|}
+\hline
+Number of features & Average percent correct \\
+\hline
+30 & 69\% \\
+\hline
+50 & 61\% \\
+\hline
+70 & 59\% \\
+\hline
+90 & 60\% \\
+\hline
+110 & 59\% \\
+\hline
+All original features & 36\% \\ \hline
+\end{tabular}
+\end{center}
+\label{tab:dimred-kfold}
+\end{table}%
+
 \end{document}

### 2011-12-06 gen_data.py

@@ -3,13 +3,6 @@ import os, sys, time
 import subprocess
 from random import choice, randint
 
-
-#sites = ["http://google.com", "http://www.facebook.com", "http://yahoo.com",
-#         "http://amazon.com", "http://wikipedia.org", "http://twitter.com", "http://ebay.com",
-#         "http://blogger.com", "http://craigslist.org", "http://linkedin.com", "http://live.com",
-#         "http://go.com", "http://msn.com", "http://bing.com", "http://espn.go.com", "http://cnn.com",
-#         "http://apple.com", "http://paypal.com", "http://aol.com"]
-
 sites = ["https://encrypted.google.com", "https://www.facebook.com", "https://twitter.com",
          "https://www.bankofamerica.com", "https://online.citibank.com", "https://www.box.net",
          "https://www.dropbox.com", "https://www.torproject.org"]

### 2011-12-06 report/paper.tex
finishing up paper

@@
 \usepackage{subfigure}
+\usepackage{url}
 \DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
@@
 %\subsection{}
+
+\abstract{
+In this project, I applied SVMs to the problem of determining the source of 
+encrypted web traffic, without seeing the content or destination of the 
+traffic. One of my main goals was to show that a proposed defense against 
+traffic analysis can be defeated by a multiclass SVM. I generated two data sets,
+and I trained and ran 
+one-vs-one and one-vs-all multiclass SVMs on these data sets. 
+I implemented a Crammer-Singer
+multiclass SVM, anomaly detection via a single-class SVM, and $k$-fold cross-validation 
+to tune parameters of all the classifiers. Along the way I designed and 
+implemented a custom feature extraction algorithm that uses one of my data sets 
+to extract features for the other.
+}
 
@@
 defense described above. While SVMs have been used before for 
-encrypted traffic analysis~\cite{SOMETHING}, the random-visit defense 
+encrypted traffic analysis~\cite{torfingerprinting}, the random-visit defense 
 is a very recent proposal and has not been well-studied yet.
@@
 have been applied to the encrypted traffic analysis problem~\cite{herrmann,liberatore}. 
-A recent work showed that SVMs are an effective traffic analysis technique~\cite{tor}, even 
+A recent work showed that SVMs are an effective traffic analysis technique~\cite{torfingerprinting}, even 
 against protocols such as Tor (an anonymity network) that employ pipelining, which makes 
@@
 \section{Data generation and preprocessing}
+\label{sec:data}
 
@@
 I implemented $k-$fold cross-validation for each SVM to choose parameters. I also used 
-cross-validation to observe how the classifier's performance improves with the addition of more data 
+cross-validation to observe how a classifier's performance improves with the addition of more data 
 and how it suffers when more classes are introduced. Data from the cross-validation process is shown 
 in Section~\ref{sec:crossvalidation}.
+
+In the closed-world setting, I used linear kernels for all three types of multi-class SVMs.
+I briefly explored using the radial basis function as a kernel in the one-versus-one multiclass 
+SVM, but I could not find parameters that outperformed the linear kernel. For example, using $k$-fold 
+cross-validation with $k=6$ and the full dimensionality multi-visit data with 30 visits per target site, the best choice of 
+parameters that I was able to find for the linear and RBF kernels led to average performance of about 
+$30\%$ correct for both kernels. Assuming that I didn't miss some better choice of parameters for the 
+RBF kernel, this result suggests that the data is mostly linearly separable with outliers: the RBF kernel 
+does no better than the linear kernel, and it can do worse by overfitting.
 
@@
 
+I implemented the primal form of the Crammer-Singer multiclass SVM~\cite{cramersinger} using the Python \texttt{cvxopt} 
+library for convex optimization. The implementation can be found in \texttt{multiclass\_svm.py} in 
+the Github repository for this project.
+
+One of the unanticipated challenges of this part of the project was that, on my laptop, \texttt{cvxopt} 
+consistently ran out of memory when solving the multiclass SVM for the full-dimensionality multi-visit data
+(which consists of 60 visits per target site). To save memory, I wrote all the training data to disk and 
+read out one vector at a time, but using \texttt{cvxopt} still requires keeping large coefficient 
+and constraint matrices in memory. To use my multiclass SVM implementation, I had to reduce the size of the 
+data to 30 visits per target site and also perform dimensionality reduction. While my dimensionality 
+reduction turned out to improve classification performance, the memory limitations meant that I couldn't 
+compare the multiclass SVM's performance on reduced dimensionality data to its performance on full 
+dimensionality data, or to other SVMs' performance on full dimensionality data.
+
 \subsection{Cross-validation for parameter tuning}
 \label{sec:crossvalidation}
+\begin{figure}
+\begin{center}
+\subfigure[One-vs-one SVM performance as the number of visits to each of the 8 target sites varies.]{
+\includegraphics[scale=0.6]{graphs/1v1_vary_data.png}
+\label{fig:vary-visits}
+}
+\subfigure[One-vs-all SVM performance as the number of target sites varies. There are 30 visits to each target site.]{
+\includegraphics[scale=0.6]{graphs/1vall_vary_labels.png}
+\label{fig:vary-labels}
+}
+\caption{$k$-fold cross-validation results (with $k=6$) as the amount of training data increases, 
+ with $c=1.0$. The training data is the multi-visit data set with 
+no dimensionality reduction.}	
+\end{center}
+\label{fig:vary-amt}
+\end{figure}
 
@@
 
+I implemented $k$-fold cross-validation to determine parameters of each SVM	, and also to verify to study how 
+SVM performance changes as the amount of training data increases. Figure~\ref{fig:vary-visits} shows how the 
+one-vs-one multiclass SVM performance increases with the number of samples for each target site. As we expect,
+performance increases somewhat linearly with the amount of training data. Figure~\ref{fig:vary-labels} shows 
+how one-vs-all multiclass SVM performance deteriorates as the number of classes increases. Though it is difficult 
+to extrapolate from the graph, we see a large fall in performance as the number of classes grows from $2$ to $4$, 
+and then a slight leveling off. Hopefully, this means that the classifier's performance scales well with the 
+number of classes and that these results are transferrable to a more realistic closed-world setting with dozens or 
+hundreds of target sites.
+
+Figure~\ref{fig:kfoldc} shows how all three multiclass SVMs perform as $c$, the cost associated with each slack 
+variable, varies. On the single-visit data set, each SVM has a clear peak for the values of $c$ that I used in the 
+experiment. After hitting the peak for the single-visit data, the performance does not seem to change much with 
+increasing $c$. This indicates that there is always some number of points that must be misclassified by a certain amount, 
+since increasing $c$ does not change the performance of the classifier. For the multi-visit data, choosing $c$ is not 
+as clear-cut: for example, in the multiclass SVM, values of $c$ as low as $0.000001$ and as high as $1.0$ appear to be 
+good choices.
+
 \subsection{Performance results and analysis}
 
-\textbf{TODO: insert perf results}
+Tables~\ref{tab:singleperf} and~\ref{tab:multiperf} show how the three multi-class SVMs perform on the single- and multi-visit data. 
+The one-vs-one multiclass SVM consistently slightly outperforms the one-vs-all SVM, both on single- and multi-visit data, with and without dimensionality reduction.
+The classifiers perform very well on the single-visit data, and they achieve almost $70\%$ accuracy on
+the multi-visit data. With 30 visits per target site and the feature vectors reduced to 50 dimensions, the multiclass classifier
+outperforms the one-vs-all and one-vs-one classifiers.
 
-I briefly explored using the radial basis function as a kernel in the one-versus-one multiclass 
-SVM, but I could not find parameters that outperformed the linear kernel. For example, using $k$-fold 
-cross-validation with $k=6$ and the multi-visit data with 30 visits per target site, the best choice of 
-parameters that I was able to find for the linear and RBF kernels led to average performance of about 
-$30\%$ correct for both kernels. Assuming that I didn't miss some better choice of parameters for the 
-RBF kernel, this result suggests that the data is mostly linearly separable with outliers: the RBF kernel 
-does no better than the linear kernel, and it can do worse by overfitting.
+\begin{table}
+\caption{Classification performance for the single-visit data set on two multiclass SVMs. (The third multiclass SVM that 
+I implemented runs out of memory on full-featured data, and my dimensionality reduction algorithm only works on 
+the multi-visit data set.) Half the data 
+is used for training and half for testing. There are $30$ visits per target site.}
+\begin{center}
+\begin{tabular}{|c|c|r|}
+\hline
+SVM & $c$ & Percent correct \\ \hline
+One-vs-one &$0.01$ & $97\%$ \\ \hline
+One-vs-all &  $0.0001$ & $94\%$ \\ \hline
+\end{tabular}
+\end{center}
+\label{tab:singleperf}
+\end{table}%
+
+\begin{table*}
+\caption{Classification performance for the multi-visit data set on three multiclass SVMs, with and without 
+dimensionality reduction. Half the data 
+is used for training and half for testing. Original features means that no dimensionality reduction was 
+performed on the data.}
+\begin{center}
+\begin{tabular}{|c|c|c|r|r|}
+\hline
+SVM & Features & Visits per target site & $c$ & Percent correct \\ \hline
+One-vs-one & original & 60 & $0.0001$ & $36\%$ \\ \hline
+One-vs-one & 50 & 60 & $0.0001$ & $69\%$ \\ \hline
+One-vs-one & 50 & 30 & $0.0001$ & $48\%$ \\ \hline
+One-vs-all & original & 60 & $0.000001$ & $33\%$ \\ \hline
+One-vs-all & 50 & 60 & $0.000001$ & $64\%$ \\ \hline
+One-vs-all & 50 & 30 & $0.000001$ & $52\%$ \\ \hline
+Multiclass & 50 & 30 & $1.0$ & $54\%$ \\ \hline
+\end{tabular}
+\end{center}
+\label{tab:multiperf}
+\end{table*}%
+
+In this small closed-world setting, therefore, the random-visit defense is not effective. While random background 
+requests do confuse a classifier trained on single-visit data, dimensionality reduction can be used to train a classifier that 
+distinguishes a target site in spite of random noise added to the packet trace.
+The reason for this, as I discuss in Section~\ref{sec:dimred}, is that the dimensionality reduction algorithm uses the single-visit data set to extract features for the multi-visit
+data set. This may not be an unrealistic scenario: for example, a censoring entity might collect single-visit data during a time 
+period in which target sites are not blocked, and then use this data to extract features for multi-visit data that is generated 
+when target sites are blocked and users are employing the random-visit defense.
 
@@
 
-For the open world setting, I implemented a single-class SVM with kernels, using the 
-\texttt{cvxopt} library.
-
-\subsection{Single-class SVM implementation}
-
-\subsection{Cross-validation for parameter tuning}
-
-\subsection{Performance results and analysis}
+For the open world setting, I implemented the dual form of a single-class SVM with kernels, using the 
+\texttt{cvxopt} library. This implementation can be found in \texttt{anomaly\_detection.py}. For each target site, I trained 
+a separate anomaly detector to recognize visits to that site as positive events, in hopes that visits to any other site 
+would register as negative events, thereby enabling the detection of visits to target sites. Unfortunately, the single-class
+SVM proved to be of little utility in this setting. Because of \texttt{cvxopt}'s memory limitations, I could only run the 
+anomaly detector on dimensionality-reduced multi-visit data. As in the closed-world setting, I performed $k$-fold cross 
+validation to tune the parameters, but I unable to find a set of parameters for either a linear or RBF kernel that resulted 
+in a high true-positive/true-negative rate and a low false-positive/false-negative rate. In this application, a low true positive 
+rate might be acceptable if the false-positive rate is also low: a censoring entity probably does not want to disrupt a large 
+percentage of Internet traffic because it has registered as a false positive on an anomaly detector for a target site, but an 
+anomaly detector that allows a censor to discover a small percentage of target site visits without disrupting other traffic 
+might be desirable.
+I therefore tuned the parameters for low false positive rates, and with an RBF kernel with $\beta=0.0000005$, $v=0.01$, and multi-visit data with 30 visits per target site, reduced to $130$ dimensions, the anomaly detector obtained an average true positive
+rate of $15\%$ with an average false positive rate of $4\%$. In future, I would like to experiment with the minimum enclosing ball 
+anomaly detector to determine if that model better fits this data.
 
@@
 \label{sec:dimred}
+
+Partly for fun, and partly out of a lack of knowledge as to what dimensionality reduction algorithm would be appropriate for this data, I 
+designed and implemented a custom feature extraction algorithm to use on the multi-visit data. My motivation for constructing a custom 
+algorithm came from two characteristics of the original multi-visit feature vectors:
+\begin{itemize}
+\item Because each feature vector represents a packet trace with random background packets inserted into it, a simple 
+feature ranking does not suffice. The importance of feature $i$ in vector $x_{1}$ is only very loosely correlated with the 
+importance of feature $i$ in vector $x_{2}$: in $x_{1}$, feature $i$ could come from a packet originating at the target site, 
+whereas in $x_2$, feature $i$ could very easily correspond to a packet originating from a random background site.
+\item I wanted to take advantage of the existence of the single-visit data to select features for the multi-visit data. 
+Intuitively, the existence of single-visit feature vectors for each target site provides a lot of information about what 
+features in a multi-visit data point are relevant to the target site.
+\end{itemize}
+
+The algorithm I implemented can be found in \texttt{dim\_reduction.py} in the project repository. The assumption made by this method 
+is that packets from the random background visit are uniformly dispersed throughout a multi-visit packet trace. For example, if a packet 
+of length $m$ is sent in the middle of a single-visit trace to \texttt{https://encrypted.google.com}, then we assume that it is 
+likely that a packet of length $m$ is sent in the middle of a multi-visit trace to \texttt{https://encrypted.google.com} and a random
+background site. To use this assumption, the algorithm ranks each packet in each multi-visit feature vector according to how similar 
+this packet is to packets in similar positions in each of the single-visit feature vectors.
+
+The feature extraction algorithm is parameterized by $b$, a number of blocks, and $\epsilon$, a window around packet lengths.
+The algorithm is given as input a feature vector $x$, a matrix of single-visit vectors $X$, and a desired number of 
+features $n$. To produce a dimensionality-reduced version of $x$ with $n$ features, the algorithm does the following:
+\begin{enumerate}
+\item Divide $x$ into $b$ blocks.
+\item For each packet $p$ in $x$:
+\begin{enumerate}
+\item $Score(p) \leftarrow 0$
+\item $i \leftarrow $ the index of the block that contains $p$
+\item For each vector $x \in X$:
+\begin{enumerate}
+\item $bx \leftarrow $ the packets in the $i^{th}$ block of $x$
+\item $Score(p) \leftarrow Score(p) + \frac{k}{m}$, where $k$ is the number of packets in $bx$ with the same direction as $p$ and with a length within $\epsilon$ of the length of $p$, and $m$ is the total number of packets in $bx$ with the same direction as $p$.
+\end{enumerate}
+\end{enumerate}
+\item Return $x' \leftarrow $ the vector with a feature for the length and direction of each of the $n$ distinct highest scoring packets
+\end{enumerate}
+
+In short, the algorithm scores each packet of each vector according to how similar it is to packets in the corresponding blocks of
+single-visit feature vectors. Different features are chosen for different vectors. The feature extraction depends only on the 
+single-visit data set, not on other multi-visit data points or on the labels.
+
+In my implementation, I precomputed the numbers of packets with each length and direction in each block of each single-visit 
+feature vector, so that running the algorithm on all the multi-visit feature vectors didn't take more than a few seconds on my 
+laptop.
+
+This algorithm seems to lead to good performance on multiclass SVMs, by picking out the few packet lengths/directions that 
+distinguish target site visits. I used $\epsilon=100$ and $b=15$, and found these parameters to work well enough.
+ In future, I would like to understand more rigorously why this algorithm works, what good choices of parameters are,
+  and if there are
+existing, well-studied alternatives that perform the same type of feature selection.
 
@@
 
+\section{Conclusions}
+
+In this project, I investigated the performance of several single- and multiclass SVMs on packet traces from visits to encrypted websites. 
+I found that the recently proposed random-visit defense against traffic analysis does not hold up, since a SVM with 
+dimensionality-reduced multi-visit data can achieve up to $70\%$ accuracy against this defense. In the future, I would like to better 
+understand the feature extraction algorithm that I designed from a rigorous standpoint, and also study how to improve anomaly detection 
+for the open-world setting of the encrypted traffic analysis problem.
+
+\bibliography{paper}
+\bibliographystyle{plain}
+
 \end{document}

### 2011-12-06 report/paper.tex
paper edits

@@
 This problem is naturally phrased as a supervised learning 
-problem. Given a set of packet traces, where each trace is labelled 
-with the website that a user visited to generate it, we would 
-like to determine the website that a user visited to generate a new, 
-unlabeled trace. The point of training such a classifier is not 
+problem. We train on a set of packet traces, where each trace is labelled 
+with the website that a user visited to generate it. Given a new,
+unlabeled trace, we would 
+like to determine the website that a user visited to generate this trace.
+ The point of training such a classifier is not 
 necessarily to make it easier for a censor to do its job, but rather 
@@
 \item \textbf{Designing and implementing a custom dimensionality reduction algorithm.} 
-Because \texttt{cvxopt} does not scale to very large problems, the feature vectors from the 
+Because \texttt{cvxopt} does not scale to very large problems~\cite{cvxoptscale}, the feature vectors from the 
 packet traces were too large to run on the multiclass and single-class SVMs that I built. 
-I designed a feature selection algorithm that uses data from website visits without the 
+I designed a feature selection algorithm (Section~\ref{sec:dimred}) similar to mutual information 
+that uses data from website visits without the 
 random-visit defense to select features for the data generated using the random-visit defense.
@@
 
-I implemented $k$-fold cross-validation to determine parameters of each SVM	, and also to verify to study how 
+I implemented $k$-fold cross-validation to determine parameters of each SVM, and also to study how 
 SVM performance changes as the amount of training data increases. Figure~\ref{fig:vary-visits} shows how the 
@@
 anomaly detector on dimensionality-reduced multi-visit data. As in the closed-world setting, I performed $k$-fold cross 
-validation to tune the parameters, but I unable to find a set of parameters for either a linear or RBF kernel that resulted 
-in a high true-positive/true-negative rate and a low false-positive/false-negative rate. In this application, a low true positive 
+validation to tune the parameters, but I was unable to find a set of parameters for either a linear or RBF kernel that resulted 
+in a high true-positive/true-negative rate and a low false-positive/false-negative rate. In this application, a low true-positive 
 rate might be acceptable if the false-positive rate is also low: a censoring entity probably does not want to disrupt a large 
@@
 The feature extraction algorithm is parameterized by $b$, a number of blocks, and $\epsilon$, a window around packet lengths.
-The algorithm is given as input a feature vector $x$, a matrix of single-visit vectors $X$, and a desired number of 
+The algorithm is given as input a multi-visit feature vector $x$, a matrix of single-visit vectors $X$, and a desired number of 
 features $n$. To produce a dimensionality-reduced version of $x$ with $n$ features, the algorithm does the following:
@@
 \item $i \leftarrow $ the index of the block that contains $p$
-\item For each vector $x \in X$:
+\item For each vector $x' \in X$:
 \begin{enumerate}
-\item $bx \leftarrow $ the packets in the $i^{th}$ block of $x$
-\item $Score(p) \leftarrow Score(p) + \frac{k}{m}$, where $k$ is the number of packets in $bx$ with the same direction as $p$ and with a length within $\epsilon$ of the length of $p$, and $m$ is the total number of packets in $bx$ with the same direction as $p$.
+\item Divide $x'$ into $b$ blocks.
+\item $bx' \leftarrow $ the packets in the $i^{th}$ block of $x'$
+\item $Score(p) \leftarrow Score(p) + \frac{k}{m}$, where $k$ is the number of packets in $bx'$ with the same direction as $p$ and with a length within $\epsilon$ of the length of $p$, and $m$ is the total number of packets in $bx'$ with the same direction as $p$.
 \end{enumerate}
 \end{enumerate}
-\item Return $x' \leftarrow $ the vector with a feature for the length and direction of each of the $n$ distinct highest scoring packets
+\item Return $x_{new} \leftarrow $ the vector with a feature for the length and direction of each of the $n$ distinct highest scoring packets
 \end{enumerate}
@@
 single-visit feature vectors. Different features are chosen for different vectors. The feature extraction depends only on the 
-single-visit data set, not on other multi-visit data points or on the labels.
+single-visit data set, not on other multi-visit data points or on the labels. This algorithm is akin to mutual information, except 
+that it operates on packets instead of individual features, and it compares each feature to features in similar regions of 
+single-visit feature vectors instead of to the corresponding feature in other multi-visit algorithms.
 
@@
 distinguish target site visits. I used $\epsilon=100$ and $b=15$, and found these parameters to work well enough.
- In future, I would like to understand more rigorously why this algorithm works, what good choices of parameters are,
+ In future, I would like to understand more rigorously why this algorithm works, what good choices of parameters are, how 
+ this algorithm is similar or dissimilar to mutual information,
   and if there are
@@
 In this project, I investigated the performance of several single- and multiclass SVMs on packet traces from visits to encrypted websites. 
-I found that the recently proposed random-visit defense against traffic analysis does not hold up, since a SVM with 
+I found that the recently proposed random-visit defense against traffic analysis does not hold up, since a SVM trained on 
 dimensionality-reduced multi-visit data can achieve up to $70\%$ accuracy against this defense. In the future, I would like to better 
